{ \fontfamily{ptm}\selectfont Error Bound Can Give Near Optimal Convergence Rate for Inexact Accelerated Proximal Gradient Method }

### 2025-11-11 Notebook LaTEX/EB is the key to IAGP/main.tex
>w<, changes

@@

        % \begin{fact}[strong epsilon subgradient sum rule]\label{fact:esp-subgrad-sum-rule}
        %     Take both $f, g: \RR^n\rightarrow \overline \RR$. 
        %     Let $\epsilon \ge 0$. 
        %     Then the epsilon subgradient sum rule states that 
        %         \partial_\epsilon[f + g](\bar x) = 
        %         \bigcup \left\lbrace
        %             \partial_{\epsilon_1} f(\bar x) + 
        %             \partial_{\epsilon_2} g(\bar x) \left|\; 
        %                 \min(\epsilon_1, \epsilon_2) \ge 0\wedge 
        %                 \epsilon_1 + \epsilon_2 = \epsilon
        %             \right.
        %         \right\rbrace
        %     Under the scenario that: $\reli\dom f \cap \reli\dom g \neq \emptyset$. 
        % \begin{remark}
        %     The above is taken from Morduchovich, Mau Nam \cite[Theorem 5.19]{mordukhovich_convex_2022}. 
        % \end{remark}

@@

        \begin{fact}[Fenchel Rockafellar duality]

@@

    \subsection{Optimizing the inexact proximal point problem}\label{sec:optz-inxt-pp-problem}

@@

            This assumption is about $(g, \omega, A)$. 

@@

@@

        \begin{fact}[French Rockafellar Duality {\cite[Proposition 15.22]{bauschke_convex_2017}}]\;\label{fact:fn-rck-duality}\\

@@

        The following fact from the literature indicates that it's sufficient to minimize the dual problem $\Psi_\lambda$ to obtain an element of the inexact proximal point operator. 
        The following fact is Proposition is from Villa et al. \cite[Theorem 5.1]{villa_accelerated_2013}. 
        \begin{fact}[minimizing dual of the proximal problem {\cite[Theorem 5.1]{villa_accelerated_2013}}]\label{fact:minimizing-dual-pp}
            Let $\bar v$ be a solution of $\Psi_\lambda$. 
            Suppose that $(v_n)_{n \ge 0}$ is a minimizing sequence for $\Psi_\lambda$. 
            Let $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$. 
            Then the following are true: 
                \item The sequence $z_n \rightarrow \bar z$ as well. 
                \item There exists a constant $K$ that depends on the sequence $z_n$, and $\Phi_\lambda$ such that for all $k \ge 0$ the inequality: 
                    \Phi_{\lambda}(z_n) - \Phi_\lambda(\bar z) 
                    &\le K \Vert z_n - \bar z\Vert 
                    \le K \sqrt{2\lambda}(\Psi_\lambda(v_n) - \Psi_\lambda(\bar v))^{1/2}. 

        \end{fact}
        We remark that the above fact translates any algorithm that optimizes the dual problem $\Psi_\lambda$ into optimizing the duality gap $\mathbf G(z_n, v_n)$ because it shows the primal is bounded by the dual through a Lipschitz-like inequality. 
        \par
        With the proof back in Villa et al. \cite[Theorem 5.1]{villa_accelerated_2013}, pay close attention to the constant $L_\Phi$ exists by the virtue of $\Psi$ being convex, and the sequence $v_n \rightarrow \bar v$ which allows the sequence $z_n \rightarrow \bar z_n$ to be bounded inside the domain of $\Phi_\lambda$. 
        By convexity, $\Phi_\lambda$ is locally Lipschitz on $\reli \dom \Phi_\lambda$, by convergence of $z_n$ the sequence is in a compact set in $\reli\dom \Phi_\lambda$ hence a Lipschitz bound with constant $K$ exists. 
        \par
        For this reason, the number of iterations of the inner loop required to achieve $\mathbf G(z_n, v_n) < \epsilon$ for a given $\epsilon$ is related to the convergence rate of the algorithms used to optimize $\Psi_\lambda(v_n)$. 
        With the theorem derived above, and using Theorem \ref{thm:dlty-gap-inxt-pp} it implies that any algorithm which can optimize function value $\Psi_\lambda$ will produce iterates sufficient to achieve $\approx_\epsilon \hprox_{\lambda g}(y)$. 
    \subsection{Literature reviews}

@@

        \todoinline{Cette proposition ira démontrer que le séquence de ``Inexact Gradient Mapping" converge. }

@@

    To accomplish let's assume that the outer loop iteration $k$ is fixed throughout this entire section.
    Now let $\lambda = (B_k + \rho_k)^{-1}$, the algorithm needs to resolve the following equivalent inexact proximal point problem: 

@@

    In this section, we will show that there exists an algorithm generating the sequences $z_n, v_n$ such that $\mathbf G_\lambda (z_n, v_n)$ converges linearly if $\Psi_\lambda$ satisfies the error bound conditions. 

@@

        We define the exact proximal gradient mapping and, gradient mapping: 

@@

    \begin{definition}[error bound]\;\label{def:err-bnd}\\
        Assume the set of minimizers $S = \argmin_{x} F \neq \emptyset$. 
        Let $\gamma> 0$, and let proximal gradient mapping $T_\tau$, gradient mapping $\mathcal G_\tau$ of $F = f + g$ as given by Definition \ref{def:pg-and-gm}. 
        Then their sum $F = f + g$ satisfies the error bound condition if there exists $\gamma > 0$ such that 

@@

    \begin{assumption}[gradient mapping error bound]\;\label{ass:pg-eb}\\

@@

    \begin{definition}[proximal gradient method]\;\label{def:ista}\\

@@

            Under this assumption, the iterates $(x_k)_{k \ge 0}$ given by Definition \ref{def:ista} satisfies for all $k \ge 0, \bar x \in S$ and $\tau \ge L$ the inequality: 

@@

@@

            This assumption is about $(g, \omega, A, y, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$. 

@@

                \item $y \in \RR^n$ is the vector of which the proximal problem is anchored at, fixed it to be an arbitrary vector. 
                \item Assume $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. The primal objective $\Phi_\lambda$ is given by \eqref{eqn:primal-pp}, and dual $\Psi_\lambda$ by \eqref{eqn:dual-pp}. This means if we let $h(v) := \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$, then $\Psi_\lambda(v) = h(v) + \omega^\star(v)$. 
                \item Next, assume $\Psi_\lambda = h + \omega^\star$ satisfies error bound condition (Assumption \ref{ass:pg-eb}) with $\Psi_\lambda = F$ and, $\gamma = \gamma_\lambda$ and $f = h$. Note that we can do this because $h$ is quadratic hence obviously Lipschitz continuous and Lipschitz smooth. 
                \item We assume in addition, the primal objective $\Phi_\lambda$ of proximal problem is $L_\Phi^\lambda$ Lipschitz continuous on its domain $\dom \Phi_\lambda = \dom (g\circ A)$. 

@@

            Let $\lambda > 0, \epsilon > 0$, and $(g, \omega, A, y, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}. 

@@

            Let the parameters $(g, \omega, A, y, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$ of a proximal problem satisfy Assumption \ref{ass:lin-cnvg-for-pp}. 
            Let $\tau$, $v_0, \epsilon$ be given by an algorithm that satisfies Definition \ref{def:ista-inner-lp} and, it generates iterates $(z_j, v_j)_{j \ge 0}$. 

@@

                \item The sequence $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item1}
                \item If we let $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_j) - \Phi_\lambda(\bar z)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item2}
                \item The duality gap has convergence $\mathbf G_\lambda(z_j, v_j) \le \mathcal O\left(\left(1 - \frac{\gamma_\lambda}{2\tau}\right)^{j/2}\right)$. \label{prop:inn-looplin-cnvg-item3}
                \item If $\mathbf G_\lambda(z_j, v_j) \le \epsilon$, then $z_j \approx_\epsilon \hprox_{\lambda g}(y)$. \label{prop:inn-looplin-cnvg-item4}

@@

            Note that $\Psi_\lambda$ satisfies error bound condition in Assumption \ref{ass:lin-cnvg-for-pp}, and Definition \ref{def:ista-inner-lp} has $\tau \ge \lambda\Vert A^TA\Vert$ which satisfies Definition \ref{def:ista} therefore the linear convergence results of Theorem \ref{thm:lin-cnvg-ista-eb} applies to $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)$. 
            Therefore, we claim: 

@@

            We will now proceed to proving \ref{prop:inn-looplin-cnvg-item2}. 
            Recall that the iterates $z_j = y - \lambda A^\top v_j$, and $\bar z = y - \lambda A^\top \bar v$, and we have Lipschitz continuity of $\Phi_\lambda$, hence Theorem \ref{fact:minimizing-dual-pp} applies, in addition since $\Phi_\lambda$ were assumed to be globally Lipschitz on $\dom \Phi_\lambda$ in Assumption \ref{ass:lin-cnvg-for-pp}, this means that we can replace $K$ regardless of $\bar v$, and convergent primal sequence $z_j \rightarrow \bar z$ with $L_\Phi^\lambda$ which gives: 
            \begin{align}\label{ineq:inn-loop-lin-cnvg-pitem2}
                    \Phi_\lambda(z_j) - \Phi_\lambda(\bar z) &\le L_\Phi^\lambda \sqrt{2\lambda}\left(
                    \Psi_\lambda(v_j) - \Psi_\lambda (\bar v)

@@

                    L_\Phi^\lambda\sqrt{2\lambda} \left(

@@

                    \right)^{j/2}\left(
                    \right)^{1/2}. 
            At (1), we used \eqref{ineq:inn-loop-lin-cnvg-pitem1}.
            To prove \ref{prop:inn-looplin-cnvg-item3}, by definition of duality gap in \eqref{eqn:duality-gap-pp} we have:
                &\underset{(1)}{=} \Phi_\lambda(z_j) + \Psi_\lambda(v_n) + 0
                &= \Phi_\lambda(z_j) + \Psi_\lambda(v_j) - \Phi_\lambda(\bar z) - \Psi_\lambda(\bar v)
                &= \Phi_\lambda(z_j)- \Phi_\lambda(\bar z) + \Psi_\lambda(v_n) - \Psi_\lambda(\bar v)

@@

                L_\Phi^\lambda \sqrt{2\lambda}\left(

@@

                \right)^{j/2}\left(
                \right)^{j}\left(
                \right)^{j/2}\left(
                    L_\Phi^\lambda \sqrt{2\lambda}\left(
                    + 
                    \right)^{j/2} (\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))
                \right)^{j/2}\left(
                    L_\Phi^\lambda \sqrt{2\lambda}
                    + 
                    (\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))^{1/2}
                    \right)^{1/2} . 
            At (1) we used strong duality because constraint qualification is in Assumption \ref{ass:for-inxt-prox}. 
            At (2) we used \eqref{ineq:inn-loop-lin-cnvg-pitem1}, \eqref{ineq:inn-loop-lin-cnvg-pitem2}. 
            To see \ref{prop:inn-looplin-cnvg-item4}, apply Theorem \ref{thm:dlty-gap-inxt-pp}. 

@@

        Some results in the literature now follow.  
        The goal of this section is to show that specific type of nonsmooth function $\omega$ that common appear in applications satisfies the error bound condition for the proximal problem, and hence the results from the previous section are applicable. 
        \begin{definition}[quasi-strongly convex function {\cite[Definition 1]{necoara_linear_2019}}]
            Let $f:\RR^n \rightarrow \RR$ be differentiable. 

@@

            It is quasi strongly-convex on the set $X \subseteq \RR^n$ if $\exists \kappa > 0$ such that $\forall x \in X$, let $\bar x = \Pi_{X^+} x$, it satisfies
                f^+ - f(x) - \langle \nabla f(x), \bar x - x\rangle + \frac{\kappa}{2}\Vert x - \bar x\Vert^2 \quad \left(\forall x \in X\right). 

@@

        \begin{definition}[quadratic growth]\label{def:q-growth}
            Let $F = f + g$ where $f: \RR^n \rightarrow \RR$ be differentiable and, $g: \RR^n \rightarrow \overline \RR$ be closed convex and, proper. 

@@

@@

            Let $f: \RR^n \rightarrow $

>>>>

    $\Pi_S$ denotes the projection onto a set $S \subseteq \RR^n$. 

@@

@@

@@

    \subsection{Optimizing an inexact proximal point problem}\label{sec:optz-inxt-pp-problem}

@@

            This assumption is about $(g, \omega, A, K_\omega, K_{\omega^\star})$. 

@@

                \item $\omega$ is $K_\omega$ Lipschitz continuous, and $\omega^\star$ is $K_{\omega^\star}$ Lipschitz continuous and in addition, $\dom \omega^\star$ is a compact set. 

@@

        \begin{fact}[Fenchel Rockafellar Duality {\cite[Proposition 15.22]{bauschke_convex_2017}}]\;\label{fact:fn-rck-duality}\\

@@

        The following theorem is enhenced from Villa et al. \cite[Theorem 5.1]{villa_accelerated_2013}. 
        % \begin{fact}[minimizing dual of the proximal problem {\cite[Theorem 5.1]{villa_accelerated_2013}}]\;\label{fact:minimizing-dual-pp}\\
        %     Let $\bar v$ be a solution of $\Psi_\lambda$. 
        %     Suppose that $(v_j)_{j \ge 0}$ is a minimizing sequence for $\Psi_\lambda$. 
        %     Let $z_j = y - \lambda A^\top v_j$, and $\bar z = y - \lambda A^\top \bar v$. 
        %     Then the following are true: 
        %     \begin{enumerate}[nosep]
        %         \item The sequence $z_j \rightarrow \bar z$ as well. 
        %         \item There exists a constant $K$ that depends on the sequence $z_j$, and $\Phi_\lambda$ such that for all $j \ge 0$ it has the inequality: 
        %             \Phi_{\lambda}(z_j) - \Phi_\lambda(\bar z) 
        %             &\le K \Vert z_j - \bar z\Vert 
        %             \le K \sqrt{2\lambda}(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))^{1/2}. 
        %     \end{enumerate}
        % We remark that the above fact translates any algorithm that optimizes the dual problem $\Psi_\lambda$ into optimizing the duality gap $\mathbf G(z_j, v_j)$ by this inequality. 
        % \par
        % With the proof back in Villa et al. \cite[Theorem 5.1]{villa_accelerated_2013}, pay close attention to the constant $L_\Phi$ exists by the virtue of $\Psi$ being convex, and the sequence $v_j \rightarrow \bar v$ which allows the sequence $z_j \rightarrow \bar z_j$ to be bounded inside the domain of $\Phi_\lambda$. 
        % By convexity, $\Phi_\lambda$ is locally Lipschitz on $\reli \dom \Phi_\lambda$, by convergence of $z_j$ the sequence is in a compact set in $\reli\dom \Phi_\lambda$ hence a Lipschitz bound with constant $K$ exists. 
        % \par
        % For this reason, the number of iterations of the inner loop required to achieve $\mathbf G(z_j, v_j) < \epsilon$ for a given $\epsilon$ is related to the convergence rate of the algorithms used to optimize $\Psi_\lambda(v_j)$. 
        % With the theorem derived above, and using Theorem \ref{thm:dlty-gap-inxt-pp} it implies that any algorithm which can optimize function value $\Psi_\lambda$ will produce iterates sufficient to achieve $\approx_\epsilon \hprox_{\lambda g}(y)$. 
        \todoinline{
            Un nouvel candidat ce que remplace le denière théorem suivant. 

        \begin{theorem}[minimizing the dual of the proximal problem]\;\label{thm:minimizing-dual-pp}\\
            Assume that we have $(g, \omega, A)$ given by Assumption \ref{ass:for-inxt-prox}. 
            Let the $\Phi_\lambda$ be given by \eqref{eqn:primal-pp}, and dual $\Psi_\lambda$ by \eqref{eqn:dual-pp}. 
            Let $\bar v$ be a minimizer of $\Psi_\lambda$ and suppose that sequence $(v_j)_{j\ge 0}$ minimizes dual $\Psi_\lambda$. 
            Then, the followings are true: 
                \item\label{thm:minimizing-dual-pp:item1} If $\bar v$ is an minimizer of dual $\Psi_\lambda$, then $\bar z = y - \lambda A^\top \bar v$ is a minimizer of primal $\Phi_\lambda$. 
                \item\label{thm:minimizing-dual-pp:item2} Let $z_j = y - \lambda A^\top v_j$, it has $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v) \ge \frac{1}{2 \lambda} \Vert z_j - \bar z\Vert^2$, and therefore it has $z_j \rightarrow \bar z$. 
                \item\label{thm:minimizing-dual-pp:item3} And, by our assumption, the primal optimality gap is bounded by dual for all $v \in \RR^m$ by the inequality: 
                    & \Phi_\lambda(z_j) - \Phi_\lambda(\bar z) 
                    \sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}\left(
                        K_\omega \Vert A\Vert 
                        + \lambda^{-1}\Vert z_j - y\Vert 
                        + \frac{1}{2\lambda}\sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}
            There are two intermediate results to prior to proving the items in the theorem. 
            In preparations, for all $v \in \RR^m$, it's obvious that we have: 
            \begin{align}\label{eqn:thm:minimizing-dual-pp:pitem1}
                    & \frac{1}{2\lambda}\left\Vert \lambda A^\top v - y\right\Vert^2
                    - \frac{1}{2\lambda}\left\Vert \lambda A^\top \bar v - y\right\Vert^2 
                    + \langle A \bar z, v - \bar v\rangle 
                    \left\Vert 
                        \lambda A^\top v - \lambda A^\top \bar v  + \lambda A^\top \bar v - y
                    - \frac{1}{2\lambda}\left\Vert \lambda A^\top \bar v - y\right\Vert^2 
                    + \langle A \bar z, v - \bar v\rangle 
                    \frac{1}{2\lambda} \left\Vert \lambda A^\top(v - \bar v)\right\Vert^2
                    + \frac{1}{\lambda}\left\langle \lambda A^\top(v - \bar v), \lambda A^\top \bar v - y \right\rangle
                    + \left\langle \bar z, A^\top(v - \bar v)\right\rangle 
                    &\underset{\text{(1)}}{=} 
                    \frac{1}{2\lambda} \left\Vert \lambda A^\top(v - \bar v)\right\Vert^2
                    - \frac{1}{\lambda}\left\langle \lambda A^\top(v - \bar v), \bar z \right\rangle
                    + \left\langle \bar z, A^\top(v - \bar v)\right\rangle 
                    &= \frac{1}{2\lambda} \left\Vert \lambda A^\top(v - \bar v)\right\Vert^2. 
            At (1), we assumed for the theorem statement that $\bar z = y - \lambda A^\top \bar v$. 
            By the optimality of $\bar v$ on the dual problem, we have the following: 
            \begin{align}\label{eqn:thm:minimizing-dual-pp:pitem2}
                    & \mathbf 0 \in 
                    A \left(\lambda A^\top \bar v - y\right) + \partial \omega^\star(\bar v)
                    A\bar z \in \partial \omega^\star(\bar v)
                    \omega^\star(v) - \omega^\star(\bar v) 
                    \ge \langle A \bar z, v_n - \bar v\rangle. 
            We will now prove \ref{thm:minimizing-dual-pp:item1}, because $A \bar z \in \partial \omega^\star (\bar v) \iff \partial \omega(A \bar z) \ni \bar v$, we can derive that $\bar z = y - \lambda A^\top \bar v$ is primal optimal because 
                y - \bar z &= \lambda A^\top \bar v \in \lambda A^\top\partial \omega (A \bar z). 
            Re-arranging yields: $\mathbf 0 \in \bar z - y + \lambda A^\top \partial \omega (A \bar z) = \partial \Phi_\lambda(\bar z)$. 
            Now we will prove \ref{thm:minimizing-dual-pp:item2}. 
            Recall that $z_j = y - \lambda A^\top v_j$, therefore it has: 
                \Phi_\lambda(v_j) - \Phi_\lambda(\bar v)
                &= \frac{1}{2\lambda}\left\Vert
                    \lambda A^\top v_j - y
                - \frac{1}{2\lambda}\left\Vert
                    \lambda A^\top \bar v - y
                + \omega^\star(v_j) - \omega^\star(\bar v)
                \frac{1}{2\lambda}\left\Vert
                    \lambda A^\top v_j - y
                - \frac{1}{2\lambda}\left\Vert
                    \lambda A^\top \bar v - y
                + \langle A\bar z, v_j - \bar v\rangle
                &\underset{(3)}{=} \frac{1}{2\lambda}\Vert \lambda A^\top(v_j - \bar v)\Vert^2
                &\underset{(4)}{=} \frac{1}{2\lambda}\Vert z_j - \bar z\Vert^2. 
            At (2) we used \eqref{eqn:thm:minimizing-dual-pp:pitem2}, at (3) we used \eqref{eqn:thm:minimizing-dual-pp:pitem1}. 
            At (4), we again $\bar z = y - \lambda A^\top \bar v$. 
            We have $\bar z$ being the optimal solution of primal $\Phi_\lambda$. 
            Now, if we set $v = v_j$, and then: 
                0 = \lim_{j \rightarrow \infty} \Psi_\lambda(v_j) - \Psi_{\lambda} (\bar v) \ge \lim_{j \rightarrow \infty}\Vert z_j - \bar z \Vert^2. 
            Implying that $z_j \rightarrow \bar z$ also. 
            We will now prove \ref{thm:minimizing-dual-pp:item3}. 
            We have for all $z \in \RR^n$, the following: 
                & \Phi_\lambda(z_j) - \Phi_\lambda(\bar z) 
                &= \omega(Az_j) - \omega(A \bar z)
                + \frac{1}{2\lambda}(\Vert z_j - y \Vert^2 - \Vert \bar z - y\Vert^2)
                K_\omega\Vert A\Vert \Vert z_j - \bar z\Vert 
                + \frac{1}{2\lambda}\left(
                    \Vert z_j - y\Vert + \Vert \bar z_j - y\Vert
                    \Vert z_j - y\Vert - \Vert \bar z - y\Vert
                K_\omega\Vert A\Vert \Vert z_j - \bar z\Vert 
                + \frac{1}{2\lambda}\left(
                    \Vert z_j - y\Vert + \Vert \bar z - y\Vert
                \right)\Vert z_j - \bar z\Vert
                K_\omega\Vert A\Vert \Vert z_j - \bar z\Vert 
                + \frac{1}{2\lambda}\left(
                    2\Vert z_j - y\Vert + \Vert \bar z - z_j\Vert 
                \right)\Vert z_j - \bar z\Vert
                &= \Vert z_j - \bar z\Vert\left(
                    K_\omega \Vert A\Vert 
                    + \lambda^{-1}\Vert z_j - y\Vert 
                    + \frac{1}{2\lambda}\Vert \bar z - z_j\Vert
                &\underset{\text{\ref{thm:minimizing-dual-pp:item2}}}{\le} 
                \sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}\left(
                    K_\omega \Vert A\Vert 
                    + \lambda^{-1}\Vert z_j - y\Vert 
                    + \frac{1}{2\lambda}\sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}

    \subsection{Literature reviews}

@@

        \todoinline{
            Cette proposition ira démontrer que ce séquence de ``Inexact Gradient Mapping" converge. \\
            N'oubliez pas de finir. 

@@

    Let's assume that the outer loop iteration $k$ is fixed throughout this entire section to simplify our discussion since, in this section we will only focus on the convergence rate of the inner loop for one specific iteration of the outer loop. 
    Let $\lambda = (B_k + \rho_k)^{-1}$, the algorithm needs to resolve the following equivalent inexact proximal point problem: 

@@

    We will show that there exists an algorithm generating the sequences $z_j, v_j$ such that $\mathbf G_\lambda (z_j, v_j)$ converges linearly if $\Psi_\lambda$ satisfies the error bound conditions. 

@@

        For all $\tau > 0$, we define the exact proximal gradient mapping and, gradient mapping: 

@@

    \begin{definition}[the error bound condition]\;\label{def:err-bnd}\\
        Under the same assumptions in Definition \ref{def:pg-and-gm}, the function $F = f + g$ satisfies the error bound condition if there exists $\gamma > 0$ such that 

@@

    \begin{assumption}[problem with proximal gradient and error bound]\;\label{ass:pg-eb}\\

@@

    \begin{definition}[the proximal gradient method]\;\label{def:ista}\\

@@

            Under this assumption, the iterates $(x_k)_{k \ge 0}$ given by Definition \ref{def:ista} satisfies for all $k \ge 0, \bar x \in S$ and $\tau \ge L$: 

@@

                \right)(F(x_k) - F(\bar x)), \text{where } \frac{\gamma}{2\tau} \in (0, 1)

@@

            This assumption is about $(g, \omega, A, y, \Phi_\lambda,\Psi_\lambda,\gamma_\lambda)$. 

@@

                \item\label{ass:lin-cnvg-for-pp:item1} $y \in \RR^n$ is the vector of which the proximal problem is anchored at, fixed it to be an arbitrary vector. 
                \item\label{ass:lin-cnvg-for-pp:item2} Assume $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. The primal objective $\Phi_\lambda$ is given by \eqref{eqn:primal-pp}, and dual $\Psi_\lambda$ by \eqref{eqn:dual-pp}. This means if we let $h(v) := \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$, then $\Psi_\lambda(v) = h(v) + \omega^\star(v)$. 
                \item\label{ass:lin-cnvg-for-pp:item3} Next, assume $\Psi_\lambda = h + \omega^\star$ satisfies error bound condition (Assumption \ref{ass:pg-eb}) with $\Psi_\lambda = F$ and, $\gamma = \gamma_\lambda$ and $f = h$. Note that we can do this because $h$ is quadratic hence obviously Lipschitz continuous and Lipschitz smooth. 
                % \item\label{ass:lin-cnvg-for-pp:item4} Assume that there exists the constant $C_\Psi^\lambda < \infty$ such that 
                % $$
                %     C_\Psi^\lambda = \sup_{v\in \RR^m} \Psi_\lambda(v) - \inf_{v\in \RR^m}\Psi_\lambda(v). 
                % $$
                % \item\label{ass:lin-cnvg-for-pp:item5} Assume that $\omega$ is a $K_\omega$ Lipschitz continuous function on $\dom \omega$. 

@@

            Let $\lambda > 0, \epsilon > 0$, and $(g, \omega, A, y, \Phi_\lambda,\Psi_\lambda,\gamma_\lambda)$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}. 

@@

            Let the parameters $(g, \omega, A, y, \Phi_\lambda, \Psi_\lambda, \gamma_\lambda)$ of a proximal problem satisfy Assumption \ref{ass:lin-cnvg-for-pp}. 
            Let $\tau$, $v_0, \epsilon > 0$ be given by Definition \ref{def:ista-inner-lp} along with iterates $(z_j, v_j)_{j \ge 0}$. 

@@

                \item\label{prop:inn-loop-lin-cnvg:item1} Let $\bar v$ be minimizer of $\Psi_\lambda$, the sequence $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)$ converges linearly to zero. 
                \item\label{prop:inn-loop-lin-cnvg:item2} There exists constants $K_\Psi^\lambda$ such that $\Psi_\lambda$ is $K_\Psi^\lambda$ Lipschitz continuous on $\dom \Psi_\lambda$, as a consequence there exists constant $C_\Psi^\lambda$ such that, $\sup_{v \in \RR^m}\Phi_\lambda(v) - \Phi_\lambda(\bar v) \le K_\Psi^\lambda\sup_{v \in \dom\Psi_\lambda}\Vert v - \bar v \Vert = C_\Psi^\lambda < \infty$. 
                \item\label{prop:inn-loop-lin-cnvg:item3} The duality gap has a linear convergence rate vy the inequality: 
                    \mathbf G_\lambda(z_j, v_j) \le
                    \right)^{j/2}\sqrt{2\lambda C_\Psi^\lambda}
                        K_\omega \Vert A\Vert 
                        + \lambda^{-1}\Vert z_j - y\Vert 
                        + \frac{\sqrt{2\lambda C_\Psi^\lambda}}{\lambda}
                \item\label{prop:inn-loop-lin-cnvg:item4} If $\mathbf G_\lambda(z_j, v_j) \le \epsilon$, then $z_j \approx_\epsilon \hprox_{\lambda g}(y)$. If we let $\tau = \lambda \Vert AA^\top\Vert$, then a sufficient number of iteration needed to achieve the optimality is given by: 
                \todoinline{
                    N'obliez pas de finir! 

@@

            To start, we prove \ref{prop:inn-loop-lin-cnvg:item1}. 
            Recall that it has $\Psi_\lambda = h + \omega^\star$ with $h$ being Lipschitz smooth and, $\omega^\star$ closed convex proper from item \ref{ass:lin-cnvg-for-pp:item2} in Assumption \ref{ass:lin-cnvg-for-pp}. 
            In addition $\Psi_\lambda$ also satisfies error bound in item \ref{ass:lin-cnvg-for-pp:item3} of Assumption \ref{ass:lin-cnvg-for-pp} with $\gamma = \gamma_\lambda$. 
            Finally, $(z_j, v_j)_{j \ge 0}$ given by Definition \ref{def:ista-inner-lp} has $\tau \ge \lambda\Vert A^\top A\Vert$ so it's essntially Definition \ref{def:ista} with $x_j = v_j$. 
            Therefore results from Theorem \ref{thm:lin-cnvg-ista-eb} applies with $F = \Psi_\lambda, x_j= v_j$ and it has: 

@@

            Next, we show \ref{prop:inn-loop-lin-cnvg:item2}. 
            The smooth part of $\Phi$ is the quadratic $h(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$, it's locally Lipschitz on the compact the domain of $\dom\Psi_\lambda = \dom \omega^\star$ is compact by Assumption \ref{ass:for-inxt-prox}, hence the smooth part is Lipschitz on $\dom \omega^\star$. 
            In addition, $\omega^\star$ is assumed to be Lipschitz on $\dom \omega^\star$, therefore the entire function $\Psi$ is Lipschitz on $\omega^\star$, we denote the Lipschitz constant by $K_\Psi^\lambda$. 
            Because $\omega^\star$ is bounded, therefore there exists constant $C_\Psi^\lambda$ such that.
                \sup_{v \in \RR^m}\Phi_\lambda(v) - \Phi_\lambda(\bar v) \le K_\Psi^\lambda\sup_{v \in \dom\Psi_\lambda}\Vert v - \bar v \Vert = C_\Psi^\lambda < \infty. 
            To see the duality gap, Theorem \ref*{thm:minimizing-dual-pp}\ref{thm:minimizing-dual-pp:item3} applies because $v_j$ by \eqref{ineq:inn-loop-lin-cnvg-pitem1} provides us the sequence $(v_j)_{j \ge 0}$ such $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)$ converges. 
            {\small
                &= \Phi_\lambda(z_j) - \Phi_\lambda(\bar z) + 0
                &= \Phi_\lambda(z_j) - \Phi_\lambda(\bar z) + \Psi_\lambda(v_j) - \Psi_\lambda(\bar v)
                &\le \sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}\left(
                    K_\omega \Vert A\Vert 
                    + \lambda^{-1}\Vert z_j - y\Vert 
                    + \frac{1}{2\lambda}\sqrt{2\lambda\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
                    + \Psi_\lambda(v_j) - \Psi_\lambda(\bar v)
                \sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}\left(
                    K_\omega \Vert A\Vert 
                    + \lambda^{-1}\Vert z_j - y\Vert 
                    + \frac{\sqrt{2\lambda}}{\lambda}\sqrt{\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}

@@

@@

                \right)^{j/2}\sqrt{2\lambda(\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))}
                    K_\omega \Vert A\Vert 
                    + \lambda^{-1}\Vert z_j - y\Vert 
                    + \frac{\sqrt{2\lambda}}{\lambda}\sqrt{\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}

@@

@@

                \right)^{j/2}\sqrt{2\lambda C_\Psi^\lambda}
                    K_\omega \Vert A\Vert 
                    + \lambda^{-1}\Vert z_j - y\Vert 
                    + \frac{\sqrt{2\lambda C_\Psi^\lambda}}{\lambda}
            At (1) we used \eqref{ineq:inn-loop-lin-cnvg-pitem1}. 
            At (2) we used \ref{prop:inn-loop-lin-cnvg:item2}. 
            \todoinline{
                N'obliez pas à finir la demonstration d'article (iv). 

@@

        The goal of this section is to show that specific type of nonsmooth function $\omega$ that common appear in applications satisfies the error bound condition for the proximal problem, and hence the results from the previous section are applicable and relevant to practical applications. 
        Our major results are stated in Proposition \ref{prop:1nrm-prox-problem}. 
        \begin{definition}[smooth quasi strongly convex {\cite[Definition 1]{necoara_linear_2019}}]\;\label{def:q-scnvx}\\
            Let $f:\RR^n \rightarrow \RR$ be convex, differentiable and, $L$ lipschitz smooth. 

@@

            It is smooth quasi strongly convex (SQSC) on the set $X \subseteq \RR^n$ if $\exists \kappa > 0$ such that $\forall x \in X$, let $\bar x = \Pi_{X^+} x$, it satisfies
                0 &\le f^+ - f(x) - \langle \nabla f(x), \bar x - x\rangle 
                - \frac{\kappa}{2}\Vert x - \bar x\Vert^2 \quad \left(\forall x \in X\right). 

@@

        \begin{definition}[quadratic growth condition]\;\label{def:q-grwth}\\
            Let $F = f + g$ where $f: \RR^n \rightarrow \RR$ be convex differentiable and, $g: \RR^n \rightarrow \overline \RR$ be closed convex and, proper. 

@@

        Obviously, 

@@

            Suppose $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, let $F = f + g$. 
            In addition, let's assume that
            \begin{enumerate}[nosep, label=(\roman*)]
                \item the set of minimizers $S = \argmin_{x} F\neq \emptyset$, 
                \item the function $F$ satisfies quadratic growth (Definition \ref{def:q-grwth}) with some parameter $\kappa > 0$. 
